Where Do Population III Stars Form?

### 2019-03-29 paper.tex
Adding summary of my thoughts on SA model comparison

@@

\li Greif11_Delay
\begin{enumerate}
	\item Using high resolution moving mesh simulations to show the effects of streaming velocities on the virialization of the first halo and first star formation
	\item They focus on minihalos where they expect a more pronounced effect
	\item Using AREPO, three different simulations with a side length of 500 kpc.
	\item They identify the first minihalos which exceed a virial mass of 5 $\times$ 10$^{5}$ M$_{\odot}$.
	\item They apply a relative velocity of 3 km s$^{-1}$ at z = 99.
	\item When a streaming velocity is applied, the gas fractions in their halos are reduced by about 50\%
	\item Figure 3 shows how the virial mass is increased when a streaming velocity is applied. The factor the virial mass is increased by is about 3, which results in a delay of Pop III star formation by $\delta$z $\approx$ 4
	\item With a streaming velocity, the gas temperature at the virial radius is higher
	\item The velocity dispersion is also higher with streaming velocities, which means the gas is more turbulent. They say that this could lead to a lower mass for Pop III stars than expected since fragmentation is increased
	\item The nubmer of minihalos that can cool and form stars is reduced in the case of streaming velocities. 
	\item Overall, gravitational collapse in minihalos is delayed, which means Pop III star formation is delayed, and the increased fragmentation may affect the mass function of the first stars. 
\end{enumerate}

>>>>

\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that is model dependent.  We should focus on the relationship between the LW background intensity and the halo masses.  This is the best practice because our cosmological volume is small and cannot capture the cosmic variance.  The Tegmark+ result is the absolute lowest halo mass for H2 cooling.  Trenti+ uses a similar argument as them to calculate the minimum mass that is dependent on the LW background that they calculate from their semi-analytic model.  In this discussion, I wouldn't put emphasis (e.g. in comparison with Mebane+) on our Pop III SFRD decreasing at a particular redshift because it's a small box.  In other studies (like the Renaissance and Wise12+), the Pop III SFRD is pretty flat until some later time.  None of these semi-analytic models include self-shielding.  I think it would be worthwhile to make a plot of (minimum) host halo mass and J_LW, comparining our work with others.

@@

\li Greif11\_Delay
\begin{enumerate}
	\item Using high resolution moving mesh simulations to show the effects of streaming velocities on the virialization of the first halo and first star formation
	\item They focus on minihalos where they expect a more pronounced effect
	\item Using AREPO, three different simulations with a side length of 500 kpc.
	\item They identify the first minihalos which exceed a virial mass of 5 $\times$ 10$^{5}$ M$_{\odot}$.
	\item They apply a relative velocity of 3 km s$^{-1}$ at z = 99.
	\item When a streaming velocity is applied, the gas fractions in their halos are reduced by about 50\%
	\item Figure 3 shows how the virial mass is increased when a streaming velocity is applied. The factor the virial mass is increased by is about 3, which results in a delay of Pop III star formation by $\delta$z $\approx$ 4
	\item With a streaming velocity, the gas temperature at the virial radius is higher
	\item The velocity dispersion is also higher with streaming velocities, which means the gas is more turbulent. They say that this could lead to a lower mass for Pop III stars than expected since fragmentation is increased
	\item The nubmer of minihalos that can cool and form stars is reduced in the case of streaming velocities. 
	\item Overall, gravitational collapse in minihalos is delayed, which means Pop III star formation is delayed, and the increased fragmentation may affect the mass function of the first stars. 
\end{enumerate}
